### 2023-10-11 chapters/discussion.tex
Updates to discussion

\begin{figure}
    \begin{subfigure}[c]{0.48\columnwidth}
        \centering
        \includegraphics[width=1\columnwidth]{paper_retrospective_calibration_plots/calibration_curve_ensemble_and_all_models_uncalibrated.pdf}
        % \caption{}
        % \label{fig_discussion:calibration_curve_ensemble_and_all_models_uncalibrated}
    \end{subfigure}
    % \hfill
    \begin{subfigure}[c]{0.48\columnwidth}
        \centering
        \includegraphics[width=1\columnwidth]{paper_retrospective_calibration_plots/histogram_ensemble_and_single_model.pdf}
        % \caption{}
        % \label{fig_discussion:histogram_ensemble_and_single_model}
    \end{subfigure}
    \caption[Calibration curve for the uncalibrated stroke recognition model and empirical distribution of predicted probabilities.]{%
        Calibration curve for the uncalibrated stroke recognition ensemble model (left) and the histogram of predicted probabilities (right) for the test set. 
        We use the ensemble that achieved the median F1-score reported in \cref{tab_retrospective:table3-occlusion-analysis} and \cref{fig_retrospective:figure1-roc-curve}.}
    \label{fig_discussion:retrospective-paper-calibration-curve-of-uncalibrated-model}
\end{figure}

@@

\begin{figure}
    \begin{subfigure}[c]{0.48\columnwidth}
        \centering
        \includegraphics[width=1\columnwidth]{paper_retrospective_calibration_plots/calibration_curves_ensemble.pdf}
        % \caption{}
        % \label{fig_discussion:calibration_curve_ensemble_and_all_models_uncalibrated}
    \end{subfigure}    
    % \hfill
    \begin{subfigure}[c]{0.48\columnwidth}
        \centering
        \includegraphics[width=1\columnwidth]{paper_retrospective_calibration_plots/calibration_fits_ensemble.pdf}
        % \caption{}
        % \label{fig_discussion:histogram_ensemble_and_single_model}
    \end{subfigure}    
    \caption[Calibration fits and curves for the stroke recognition model using Platt-scaling and isotonic regression for calibration.]{ Calibration curves using sigmoid and isotonic calibration fits for the stroke recognition ensemble model (left) and the calibration fits (right) for the test set. We use the ensemble that achieved the median F1-score reported in \cref{tab_retrospective:table3-occlusion-analysis} and \cref{fig_retrospective:figure1-roc-curve}.}
    \label{fig_discussion:retrospective-paper-calibration-curve-sigmoid-isotonic}
\end{figure}

Clinicians in intensive care units and emergency departments have been found to strongly agree that a singular focus on overall accuracy cannot ensure sustained use of and trust in a model \cite{tonekaboni_what_2019}. Clinicians expect an alert to present a prediction that aligns with patient status. Despite expert-agreed thresholds for when alerts should be triggered, however, many alerts may not be aligned since the unbalanced and ambiguous nature of many predictive problems in healthcare can lead to low predictive precision \parencite{umscheid_development_2015, cite14, cite15, wenstrup_retrospective_2023}. This can lead to alarm fatigue \parencite{embi_evaluating_2012} and can undermine the use and endorsement by clinicians of such systems \parencite{guidi_clinician_2015}. 
The expected precision of the stroke recognition model of $24.9\%$ (95\% confidence interval $24.3-25.5\%)$ means it might be wrong three out of four times it predicts a positive. This unfortunately makes alarm fatigue likely among its potential users which might diminish it's real-world impact.

If the stroke recognition model were to be deployed in a randomized controlled trial, such issues might be alleviated by incorporating the calibrated probabilities in the alerts presented to users. With calibrated probabilities, user would be able to discern between certain and uncertain model predictions or might be presented only with predictions that exceed a specific confidence level. Similar approaches have been suggested by clinicians and interviews indicate that predictive uncertainty is perceived as a sort of explanation that complements the prediction \cite{tonekaboni_what_2019}.

% \begin{figure}
%     \centering
%     \includegraphics[width=0.5\textwidth]{paper_retrospective_calibration_plots/agreement_fraction.pdf}
%     \caption[Fractional agreement between stroke recognition model and call-takers as function of predicted probability]{ The fractional agreement between the stroke recognition model and the call-takers as a function of the probability predicted by the model. Both the uncalibrated and the isotonically calibrated model agree more with call-takers towards low and high probabilities. Logistic calibration yielded almost identical results to isotonic.}
%     \label{fig_discussion:retrospective-paper-fractional-agreement-vs-probability}
% \end{figure}

\begin{figure}
    \centering
    \includegraphics[width=0.5\textwidth]{paper_retrospective_calibration_plots/f1_score_ratio.pdf}
    \caption[]{}
    \label{fig_discussion:retrospective-paper-f1-score-ratio}
\end{figure}

@@

\todo[inline]{Finish this sentence and analysis.}
Making matters worse, the most certain model predictions are the ones that agree the most with call-taker judgment (see \cref{fig_discussion:retrospective-paper-fractional-agreement-vs-probability}). Hence, keeping the most certain predictions also means reducing the potential for changing call-taker.. Not really if when the model disagrees at low prob it is always right while when it disagrees at high prob it is always wrong (although unlikely and contrary to calibration - but that was done for the total set of predictions, not subgroups)

>>>>

\begin{figure}
    \begin{subfigure}[c]{0.48\columnwidth}
        \centering
        \includegraphics[width=1\columnwidth]{paper_retrospective_calibration_plots/calibration_curve_ensemble_and_all_models_uncalibrated.pdf}
        % \caption{}
        % \label{fig_discussion:calibration_curve_ensemble_and_all_models_uncalibrated}
    \end{subfigure}
    % \hfill
    \begin{subfigure}[c]{0.48\columnwidth}
        \centering
        \includegraphics[width=1\columnwidth]{paper_retrospective_calibration_plots/histogram_ensemble_and_single_model.pdf}
        % \caption{}
        % \label{fig_discussion:histogram_ensemble_and_single_model}
    \end{subfigure}
    \caption[Calibration curve for the uncalibrated stroke recognition ensemble and empirical distribution of predicted probabilities.]{%
        Calibration curve for the uncalibrated stroke recognition ensemble (left) and the histogram of predicted probabilities (right) for the test set. 
        We use the ensemble that achieved the median F1-score reported in \cref{tab_retrospective:table3-occlusion-analysis} and \cref{fig_retrospective:figure1-roc-curve}.}
    \label{fig_discussion:retrospective-paper-calibration-curve-of-uncalibrated-model}
\end{figure}

@@

\begin{figure}
    \begin{subfigure}[c]{0.48\columnwidth}
        \centering
        \includegraphics[width=1\columnwidth]{paper_retrospective_calibration_plots/calibration_curves_ensemble.pdf}
        % \caption{}
        % \label{fig_discussion:calibration_curve_ensemble_and_all_models_uncalibrated}
    \end{subfigure}    
    % \hfill
    \begin{subfigure}[c]{0.48\columnwidth}
        \centering
        \includegraphics[width=1\columnwidth]{paper_retrospective_calibration_plots/calibration_fits_ensemble.pdf}
        % \caption{}
        % \label{fig_discussion:histogram_ensemble_and_single_model}
    \end{subfigure}    
    \caption[Calibration fits and curves for the stroke recognition ensemble using Platt-scaling and isotonic regression for calibration.]{ Calibration curves using sigmoid and isotonic calibration fits for the stroke recognition ensemble model (left) and the calibration fits (right) for the test set. We use the ensemble that achieved the median F1-score reported in \cref{tab_retrospective:table3-occlusion-analysis} and \cref{fig_retrospective:figure1-roc-curve}.}
    \label{fig_discussion:retrospective-paper-calibration-curve-sigmoid-isotonic}
\end{figure}

Clinicians in intensive care units and emergency departments have been found to strongly agree that a singular focus on overall accuracy cannot ensure sustained use of and trust in a model \cite{tonekaboni_what_2019}. Clinicians expect an alert to present a prediction that aligns with patient status. Despite expert-agreed thresholds for when alerts should be triggered, however, many alerts may not be aligned since the unbalanced and ambiguous nature of many predictive problems in healthcare can lead to low predictive precision \parencite{umscheid_development_2015, cite14, cite15, wenstrup_retrospective_2023}. This can lead to alarm fatigue \parencite{embi_evaluating_2012} and can undermine the use and endorsement by clinicians of such systems \parencite{guidi_clinician_2015}. 
The expected precision of the stroke recognition ensemble of $24.9\%$ (95\% confidence interval $24.3-25.5\%)$ means it might be wrong three out of four times it predicts a positive. This unfortunately makes alarm fatigue likely among its potential users which might diminish it's real-world impact.

If the stroke recognition ensemble were to be deployed in a randomized controlled trial, such issues might be alleviated by incorporating the calibrated probabilities in the alerts presented to users. With calibrated probabilities, user would be able to discern between certain and uncertain model predictions or might be presented only with predictions that exceed a specific confidence level. Similar approaches have been suggested by clinicians and interviews indicate that predictive uncertainty is perceived as a sort of explanation that complements the prediction \cite{tonekaboni_what_2019}.

\begin{figure}
    \begin{subfigure}[c]{0.48\columnwidth}
        \centering
        \includegraphics[width=1\columnwidth]{paper_retrospective_calibration_plots/f1_score_vs_predicted_probability_ensemble_calltaker}
        % \caption{}
        % \label{fig_discussion:calibration_curve_ensemble_and_all_models_uncalibrated}
    \end{subfigure}    
    % \hfill
    \begin{subfigure}[c]{0.48\columnwidth}
        \centering
        \includegraphics[width=1\columnwidth]{paper_retrospective_calibration_plots/predicted_probability_histogram.pdf}
        % \caption{}
        % \label{fig_discussion:histogram_ensemble_and_single_model}
    \end{subfigure}    
    \caption[Comparison of F1-score of stroke recognition ensemble and call-takers as function of predicted probability.]{ Comparison of the F1-score of the stroke recognition ensemble and call-takers. The F1-score is computed on subsets of the test dataset made by binning on the calibrated probabilities of the ensemble. We see that the relative performance improvement of the ensemble over call-takers is higher towards more certain predictions. We use the ensemble that achieved the median F1-score reported in \cref{tab_retrospective:table3-occlusion-analysis} and \cref{fig_retrospective:figure1-roc-curve}.}
    \label{fig_discussion:retrospective-paper-calibration-curve-sigmoid-isotonic}
\end{figure}

Inspecting the

\todo[inline]{Finish this sentence and analysis.}

@@

\todo[inline]{Finish this sentence and analysis.}

Making matters worse, the most certain model predictions are the ones that agree the most with call-taker judgment (see \cref{fig_discussion:retrospective-paper-fractional-agreement-vs-probability}). Hence, keeping the most certain predictions also means reducing the potential for changing call-taker.. Not really if when the model disagrees at low prob it is always right while when it disagrees at high prob it is always wrong (although unlikely and contrary to calibration - but that was done for the total set of predictions, not subgroups)
